---
title: "R Notebook"
output: html_notebook
---
#   Computes the yield to maturity of a bond paying semi-annual
#   coupon payments
#
#   price, coupon payment, and time to maturity (in years)
#   are set below
#
#   Uses the function "bondvalue"
#
#spline()
Perform cubic (or Hermite) spline interpolation of given data points, returning either a list of points obtained by the interpolation or a function performing the interpolation.
xout: y=1200, x=ytm


price > par ⇒ coupon rate > current yield > yield to maturity.

```{r YTM}
bondvalue = function(c,T,r,par) 
{
  #
  #   Computes bv = bond values (current prices) corresponding
  #       to all values of yield to maturity in the
  #       input vector r
  #
  #       INPUT
  #        c = coupon payment (semi-annual)
  #        T = time to maturity (in years)
  #        r = vector of yields to maturity (semi-annual rates)
  #        par = par value
  #
  bv = c/r + (par - c/r) * (1+r)^(-2*T)
  bv
}
price = 1200    #   current price of the bond
C = 40          #   coupon payment
T= 30           #   time to maturity
par = 1000      #   par value of the bond

r = seq(.02,.05,length=300)
value = bondvalue(C,T,r,par) 
yield2M = spline(value,r,xout=price) 
plot(r,value,xlab='yield to maturity',ylab='price of bond',type="l",
     main="par = 1000, coupon payment = 40, T = 30",lwd=2)
abline(h=1200,col="red")
abline(v=yield2M,col="red")
```
!!!!
year = 1900 + rates[1:n,1:3] %*% c(1/12, 1/365 , 1) -1/12
%*%表示通常意义下的两个矩阵的乘积,要求第一个矩阵的行数与第二个矩阵列数相等。
```{r term structure}
setwd("/Volumes/win/intern/statfe/datasets")
#As an alternative to interpolation, the yield to maturity can be found using a nonlinear root finder (equation solver) such as uniroot(), which is illustrated here:
uniroot(function(r) bondvalue(C,T,r,par) - price, c(0.001,.1))

################################################
#####  Code for figure 3.2  ####################
################################################
rates = as.matrix(read.table("WeeklyInterest.txt",header=F))
head(rates)
ff = rates[,4]/100
tb03 = rates[,5]/100
cm10 = rates[,6]/100
cm30 = rates[,7]/100
tail(cm30,5)
head(cm10,5)
n=length(ff)
year = 1900 + rates[1:n,1:3] %*% c(1/12, 1/365 , 1) -1/12
#pdf("threerates.pdf",width=6,height=5) # Fig 3.2
plot(year,tb03,type="l",xlim=c(1978,1994),lwd=3,ylab="rate",lty=2)
lines(year[cm30>0],cm10[cm30>0],lty=1,lwd=2,col="red")
lines(year[cm30>0],cm30[cm30>0],lty=3,lwd=4,col="blue")
legend("topright",c("3-month","10-year","30-year"),lty=c(2,1,3),lwd=c(3,2,4),
       col=c("black","red","blue"))
```
R’s fEcofin package had many interesting financial data sets but is no longer available.
The data sets mk.maturity.csv and mk.zero2.csv used in this example were taken from this package and are now available on this book’s webpage. The data set mk.zero2 has yield curves of U.S. zero coupon bonds recorded monthly at 55 maturities. These maturities are in the data set mk.maturity. The following code plots the yield curves on four consecutive months.
```{r yield curve}
setwd("/Volumes/win/intern/statfe/datasets")
 mk.maturity = read.csv("mk.maturity.csv", header = T)
   mk.zero2 = read.csv("mk.zero2.csv", header = T)
   plot(mk.maturity[,1], mk.zero2[5,2:56], type = "l",
     xlab = "maturity", ylab = "yield")
   lines(mk.maturity[,1], mk.zero2[6,2:56], lty = 2, type = "l")
   lines(mk.maturity[,1], mk.zero2[7,2:56], lty = 3, type = "l")
   lines(mk.maturity[,1], mk.zero2[8,2:56], lty = 4, type = "l")
   legend("bottomright", c("1985-12-01", "1986-01-01",
      "1986-02-01", "1986-03-01"), lty = 1:4)
```

Plot the yield curves from December 1, 1986 to March 1, 1987 and describe how the yield curve changes during this period.
The next set of code estimates the forward rate for 1month. Line 1 es-
timates the integrated forward rate, called intForward.
r(n)=n*yn-(n-1)yn-1=diff(intForward)


```{r}
intForward = mk.maturity[,1]*mk.zero2[6,2:56]
xout=seq(0,20,length=200)
z1=spline(mk.maturity[,1],intForward,xout=xout)
forward = diff(z1$y)/diff(z1$x)
T_grid = (xout[-1]+xout[-200])/2
plot(T_grid,forward,type="l",lwd=2,ylim=c(0.06,0.11))


intForward = mk.maturity[,1]*mk.zero2[7,2:56]
z1=spline(mk.maturity[,1],intForward,xout=xout)
forward = diff(z1$y)/diff(z1$x)
lines(T_grid,forward,type="l",lwd=2,lty=2)

intForward = mk.maturity[,1]*mk.zero2[8,2:56]
z1=spline(mk.maturity[,1],intForward,xout=xout)
forward = diff(z1$y)/diff(z1$x)
lines(T_grid,forward,type="l",lwd=2,lty=3)

intForward = mk.maturity[,1]*mk.zero2[9,2:56]
z1=spline(mk.maturity[,1],intForward,xout=xout)
forward = diff(z1$y)/diff(z1$x)
lines(T_grid,forward,type="l",lwd=2,lty=4)

legend("bottomright",c("1985-12-01", "1986-01-01",
                       "1986-02-01", "1986-03-01"),lty=1:4,lwd=2)

```

