---
title: "MDS"
author: "Wj"
date: "2018/2/26"
output: html_document
---
swiss data that contains fertility and socio-economic data on 47 French speaking provinces in Switzerland.
```{r data}
data("swiss")
str(swiss)
head(swiss)
```

dist(x, method = "euclidean", diag = FALSE, upper = FALSE, p = 2)

This function computes and returns the distance matrix computed by using the specified distance measure to compute the distances between the rows of a data matrix.
method	
the distance measure to be used. This must be one of "euclidean", "maximum", "manhattan", "canberra", "binary" or "minkowski". Any unambiguous substring can be given.

cmdscale()
Classical multidimensional scaling (MDS) of a data matrix. Also known as principal coordinates analysis
cmdscale(d, k = 2, eig = FALSE, add = FALSE, x.ret = FALSE,
         list. = eig || add || x.ret)
k:the maximum dimension 
```{r classical MDS}
library(magrittr)
library(dplyr)
library(ggpubr)
# Cmpute MDS
mds <- swiss %>%
  dist() %>%          
  cmdscale() %>%
  as_tibble()
colnames(mds) <- c("Dim.1", "Dim.2")
# Plot MDS
ggscatter(mds, x = "Dim.1", y = "Dim.2",
          label = rownames(swiss),
          size = 1,
          repel = TRUE)
```

## mutate
mutate() adds new variables and preserves existing; transmute() drops existing variables.
##as_tibble
as_tibble is a new S3 generic with more efficient methods for matrices and data frames.faster than as.data.frame


```{r k-means clustering, echo=FALSE}
clust <- kmeans(mds, 3)$cluster %>%
  as.factor()
clust
mds <- mds %>%
  mutate(groups = clust)
mds
# Plot and color by groups
ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(swiss),
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

nonmetric
#Kruskal’s non-metric multidimensional scaling
```{r}
library(MASS)
mds <- swiss %>%
  dist() %>%          
  isoMDS() %>%
  .$points %>%
  as_tibble()
colnames(mds) <- c("Dim.1", "Dim.2")
# Plot MDS
ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(swiss),
          size = 1,
          repel = TRUE)

```
#Sammon’s non-linear mapping:
```{r}
library(MASS)
mds <- swiss %>%
  dist() %>%          
  sammon() %>%
  .$points %>%
  as_tibble()
colnames(mds) <- c("Dim.1", "Dim.2")
# Plot MDS
ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(swiss),
          size = 1,
          repel = TRUE)
```

