---
title: "R Notebook"
output: html_notebook
---
The data set Stock_bond.csv contains daily volumes and adjusted closing (AC) prices of stocks and the S&P 500 (columns B–W) and yields on bonds (columns X–AD) from 2-Jan-1987 to 1-Sep-2006.

ton within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
points are plotted with the character “o”. To plot a line instead, use, for example plot(GM_AC, type = "l"). Similarly, plot(GM_AC, type = "b") plots both points and a line.
```{r}
setwd("/Volumes/win/intern/statfe/datasets")
dat = read.csv("Stock_bond.csv",header=TRUE)
names(dat)
str(dat)
attach(dat)
head(dat)
par(mfrow=c(2,2))
plot(GM_AC,type="l")
plot(F_AC,type="o")
plot(X1.year.Treasury.Constant.Maturity.Rate,type="1")
plot(X10.year.Treasury.Constant.Maturity.Rate,type="1")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 
```{r return plot}
n = dim(dat)[1]
GMReturn = GM_AC[2:n]/GM_AC[1:(n-1)] - 1
FReturn = F_AC[2:n]/F_AC[1:(n-1)] - 1

#pdf("ReturnsLab01.pdf",width=6,height=5)
par(mfrow=c(1,1))
plot(GMReturn,FReturn)
#graphics.off()
MSFTReturn = MSFT_AC[-1]/MSFT_AC[-n] - 1
MRKReturn = MRK_AC[-1]/MRK_AC[-n] - 1
plot(MSFTReturn,MRKReturn)
round(cor(MSFTReturn,MRKReturn),3)
```
Suppose a hedge fund owns $1,000,000 of stock and used $50,000 of its own capital and $950,000 in borrowed money for the purchase. Suppose that if the value of the stock falls below $950,000 at the end of any trading day, then the hedge fund will sell all the stock and repay the loan. This will wipe out its $50,000 investment. 
The hedge fund is said to be leveraged 20:1 since its position is 20 times the amount of its own capital invested.
Suppose that the daily log returns on the stock have a mean of 0.05/year and a standard deviation of 0.23/year. 253 trading days
What is the probability that the value of the stock will be below $950,000 at the close of at least one of the next 45 trading days? 

```{r simulation}
rm(list=ls(all=TRUE))
niter = 1e5
below = rep(0,niter)#先初始化
profit= rep(0,niter)
set.seed(2009)
options(warn=-1)
for (i in 1:niter)
{
  r = rnorm(100,mean=.05/253,sd=.23/sqrt(253))
  logPrice = log(1e6) + cumsum(r)#本金&return
  minlogP = min(logPrice)
  below[i] = as.numeric(minlogP < log(950000))

}
#
mean(r)
mean(below)
mean(profit)
```
What is the probability that the hedge fund will make a profit of at least $100,000?

```{r}
?rnorm
rep(0, 2)
rep(1:4, each = 2)       # not the same.
rep(1:4, c(2,2,2,2))     # same as second.
rep(1:4, c(2,1,2,1))
```
In this section you will use simulations to see how stock prices evolve when the log-returns are i.i.d. normal, which implies that the price series is a geometric random walk.
There are 253 trading days per year, so you are simulating 1 year of daily returns nine times. The price starts at 120.


```{r}

set.seed(2012)
n = 253
#pdf("FigA1.pdf",width = 6, height=6)  ########## Fig A.1
par(mfrow=c(3,3))
for (i in (1:9))
{
  logr = rnorm(n,0.05/253,0.2/sqrt(253))
  price = c(120,120*exp(cumsum(logr)))
  plot(price,type="b")
}
#graphics.off()
```


